# Market evaluation {#market}

## Market capitalization^[Data are from [World Bank](https://data.worldbank.org/indicator/CM.MKT.LCAP.CD?view=chart). Only the previous 5-year period for which top 3 countries' data are available is shown.]

```{r}
country_ranking = read_html("https://www.worldometers.info/gdp/gdp-by-country/", which = 1, header = T) %>% pull(Country)

download.file("https://api.worldbank.org/v2/en/indicator/CM.MKT.LCAP.CD?downloadformat=csv", destfile = "marketcap.zip", mode = "wb")

marketcap_csv = unzip("marketcap.zip", list = T) %>% pull(Name) %>% str_subset("^(?!Metadata)")

unzip("marketcap.zip", files = marketcap_csv, overwrite = T, exdir = "marketcap")

marketcap = read_csv(file.path("marketcap", marketcap_csv), skip = 4, col_names = T, trim_ws = T)

marketcap %<>% mutate(`Country Name` = str_replace_all(`Country Name`, c("Russian Federation" = "Russia",
                                                                         "Korea, Rep." = "South Korea",
                                                                         "Korea, Dem. People's Rep." = "North Korea"))) %>% 
  select(-c(`Country Code`, `Indicator Name`, `Indicator Code`)) %>%
  pivot_longer(-`Country Name`, names_to = "Year", values_to = "Marketcap") %>%
  mutate(Year = as.numeric(Year)) %>%
  filter(Year >= (thisyear - 5) & `Country Name` %in% country_ranking)

notNA_year = marketcap %>% group_by(Year) %>% summarise(notNA = sum(!is.na(Marketcap))) %>% filter(notNA > 0) %>% pull(Year)

marketcap %<>%
  filter(Year %in% notNA_year) %>%
  mutate(Marketcap = ifelse(is.na(Marketcap), 0, Marketcap)) %>%
  group_by(Year) %>%
  mutate(Proportion = Marketcap/sum(Marketcap)) %>%
  ungroup

top_country = marketcap %>% arrange(desc(Marketcap), desc(Year), desc(`Country Name`)) %>% pull(`Country Name`) %>% unique %>% .[1:3]
notNA_year = marketcap %>% filter(`Country Name` %in% top_country & Marketcap > 0) %>% count(Year) %>% filter(n == length(top_country)) %>% pull(Year)

major_country = marketcap %>% 
  filter(Year %in% notNA_year & Proportion > 0) %>%
  group_by(`Country Name`) %>% 
  summarise(min_Proportion = min(Proportion)) %>% 
  filter(min_Proportion >= 0.001) %>% 
  pull(`Country Name`)

notNA_country = marketcap %>% group_by(`Country Name`) %>% summarise(notNA = sum(Marketcap > 0)) %>% filter(notNA > 0) %>% pull(`Country Name`)

marketcap %<>%
  filter(`Country Name` %in% major_country & Year %in% notNA_year) %>%
  mutate(Proportion = ifelse(Proportion == 0, "No data", make_percent(Proportion, 100))) %>%
  arrange(desc(Marketcap), desc(Year), desc(`Country Name`))

country_level = rev(unique(marketcap$`Country Name`))

marketcap %<>% mutate(`Country Name` = factor(`Country Name`, levels = country_level))
```

```{r, fig.width = 7, fig.height = (nrow(marketcap)/length(notNA_year) + 2)/4, fig.cap = str_c("Market capitalization of listed domestic companies across ", length(country_level), " major countries (proportion of the global market capitalization shown on the right side of each column)")}
marketcap %>% 
  ggplot(mapping = aes(x = `Country Name`, y = Marketcap/1e12)) +
  geom_col(fill = brewer_pal("qual", 4)(2)[2], color = "black", width = 0.7) +
  geom_text(mapping = aes(y = Marketcap/1e12 + 0.5, label = Proportion), hjust = 0, size = 10 / .pt, family = "Lato") + 
  scale_y_continuous(expand = c(0, 0), limits = c(0, max(marketcap$Marketcap/1e12) * 1.3)) +
  coord_flip() +
  labs(x = NULL, y = "Market capitalization (trillion USD)") +
  theme(axis.ticks.y = element_blank()) +
  facet_grid(cols = vars(Year))
```

## GDP and Buffett indicator^[Data are retrieved from [Gurufocus.com](https://www.gurufocus.com/global-market-valuation.php).]

```{r}
Buffett = read_html("https://www.gurufocus.com/global-market-valuation.php", which = 3, header = T) %>% 
  mutate(across(-c(Country, `Country ETF`), as.numeric))
```

```{r, fig.cap = str_c("GDP and Buffett indicator across ", nrow(Buffett), " major countries")}
my_datatable(Buffett, paging = T, pageLength = 10, scrollY = NULL, caption = NULL)
```

## Market valuation^[Source data and details can be found at [Gurufocus.com](https://www.gurufocus.com/global-market-valuation.php).]

```{r}
USA = read_html("https://www.gurufocus.com/stock-market-valuations.php", which = 3, header = T) %>% 
  mutate(Country = "USA")

country_mapping = c(China = "CHN", Japan = "JPN", Germany = "DEU", India = "IND", UK = "GBR", France = "FRA", Italy = "ITA", Canada = "CAN", Korea = "KOR", Australia = "AUS", Spain = "ESP", Russia = "RUS")

plan(multisession)

Others = country_mapping %>% future_imap_dfr(~read_html(str_c("https://www.gurufocus.com/global-market-valuation.php?country=", .x), 
                                                            which = 3, header = T) %>% 
                                               mutate(Country = .y))

plan("default")

All = bind_rows(USA, Others)

names(All) %<>% str_trim

col = brewer_pal("div", 5)(5)

All %<>% 
  filter(`Ratio = Total Market Cap / GDP` %>% str_detect("Where are we today")) %>%
  mutate(Valuation = str_extract(Valuation, "(Significantly|Modestly|Fair) (Overvalued|Undervalued|valued)")) %>%
  select(-`Ratio = Total Market Cap / GDP`) %>%
  left_join(Buffett %>% select(Country, `Total Market/GDP Ratio (%)`, `GDP ($Trillion)`)) %>%
  rename(`Total Market/GDP Ratio` = "Total Market/GDP Ratio (%)") %>%
  mutate(Country = factor(Country, levels = rev(Country)),
         `Total Market/GDP Ratio` = `Total Market/GDP Ratio`/100,
         Valuation = str_to_sentence(Valuation) %>% factor(levels = c("Significantly overvalued", 
                                                                      "Modestly overvalued",
                                                                      "Fair valued",
                                                                      "Modestly undervalued",
                                                                      "Significantly undervalued")))
```

```{r, fig.width = 7, fig.height = (nrow(All) + 2)/4, fig.cap = str_c("Market valuation for ", nrow(All), " major countries")}
f1 = All %>% 
  ggplot(mapping = aes(x = Country, y = `GDP ($Trillion)`)) +
  geom_col(fill = brewer_pal("qual", 4)(2)[2], color = "black", width = 0.7) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, max(All$`GDP ($Trillion)`) * 1.05)) +
  coord_flip() +
  labs(x = NULL) +
  theme(axis.ticks.y = element_blank())

f2 = All %>% 
  ggplot(mapping = aes(x = Country, y = `Total Market/GDP Ratio`)) +
  geom_col(mapping = aes(fill = Valuation), color = "black", width = 0.7) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, max(All$`Total Market/GDP Ratio`) * 1.05), labels = percent) +
  scale_fill_brewer(type = "qual", palette = 4, guide = guide_legend(title = NULL)) +
  coord_flip() +
  labs(x = NULL) +
  theme(axis.ticks.y = element_blank())

ggarrange(f1, f2, nrow = 1, legend = "right", common.legend = T)
```

## Projected annual return^[Source data and details can be found at [Gurufocus.com](https://www.gurufocus.com/global-market-valuation.php).]

```{r}
Project = read_html("https://www.gurufocus.com/global-market-valuation.php", which = 1, header = T) %>% 
  rename(Country = "") %>% 
  rename(`Projected Annual Return` = "Projected Annual Return (%)") %>%
  filter(Country != "Emerging Market:") %>%
  mutate(Country = factor(Country, levels = rev(Country)),
         `Projected Annual Return` = str_replace(`Projected Annual Return`, "%", "") %>% as.numeric %>% divide_by(100))

cutoff = max(which(Project$Country %>% rev %>% as.character %in% c("Turkey", "Indonesia", "Mexico", "Russia", "India", "China", "Brazil"))) + 0.5
```

```{r, fig.width = 7, fig.height = (nrow(Project) + 2)/4, fig.cap = "Projected future annual returns of the world's 18 largest stock markets, calculated using (1) future business growth estimates, (2) dividends, and (3) change in market valuation"}
Project %>% ggplot(mapping = aes(x = Country, y = `Projected Annual Return`)) +
  annotation_custom(rectGrob(gp = gpar(col = "black", fill = "transparent")), xmin = cutoff) +
  annotation_custom(rectGrob(gp = gpar(col = "black", fill = "transparent")), xmax = cutoff) +
  annotation_custom(textGrob("Developed market", x = unit(0.95, "npc"), hjust = 1, vjust = -2, gp = gpar(fontface = "bold")),
                    xmin = cutoff, xmax = cutoff) +
  annotation_custom(textGrob("Emerging market", x = unit(0.95, "npc"), hjust = 1, vjust = -2, gp = gpar(fontface = "bold")),
                    xmin = -Inf, xmax = -Inf) +
  geom_col(mapping = aes(fill = factor(sign(`Projected Annual Return`))), color = "black", width = 0.7) +
  scale_y_continuous(breaks = pretty_breaks(), labels = percent) +
  scale_fill_manual(breaks = c("-1", "1", "0"), values = brewer_pal("qual", 4)(3), guide = F) +
  coord_flip() +
  labs(x = NULL) +
  theme(axis.ticks.y = element_blank())
```
