# Market evaluation {#market}

## Market capitalization[^1]

```{r}
if (thishour == 0) {
  download.file("https://api.worldbank.org/v2/en/indicator/CM.MKT.LCAP.CD?downloadformat=csv", destfile = "marketcap.zip", mode = "wb")
  unzip("marketcap.zip", overwrite = T, exdir = "marketcap")
  
  tryCatch(
    {
      download.file("https://api.worldbank.org/v2/en/indicator/NY.GDP.MKTP.CD?downloadformat=csv", destfile = "gdp.zip", mode = "wb")
    },
    error = function(cond) {
      message(cond)
      return(NULL)
    })
  unzip("gdp.zip", overwrite = T, exdir = "gdp")
}
```

```{r}
gdp_ranking = read_html("https://www.worldometers.info/gdp/gdp-by-country/", which = 1, header = T) %>% pull(Country)

marketcap_csv = unzip("marketcap.zip", list = T) %>% pull(Name) %>% str_subset("^(?!Metadata)")
marketcap = read_csv(file.path("marketcap", marketcap_csv), skip = 4, col_names = T, trim_ws = T)

rename_country1 = function(x) {
  mapping = c("Czech Republic (Czechia)" = "Czech",
              "Côte d'Ivoire" = "Cote d'Ivoire")
  
  ifelse(x %in% names(mapping), mapping[x], x)
}

rename_country2 = function(x) {
  mapping = c("Russian Federation" = "Russia",
              "Korea, Rep." = "South Korea",
              "Korea, Dem. People's Rep." = "North Korea",
              "Iran, Islamic Rep." = "Iran",
              "Hong Kong SAR, China" = "Hong Kong",
              "Egypt, Arab Rep." = "Egypt",
              "Czech Republic" = "Czech",
              "Slovak Republic" = "Slovakia",
              "Macao SAR, China" = "Macao",
              "Congo, Dem. Rep." = "DR Congo",
              "Congo, Rep." = "Congo",
              "Yemen, Rep." = "Yemen",
              "Lao PDR" = "Laos",
              "Bahamas, The" = "Bahamas",
              "Brunei Darussalam" = "Brunei")
  
  ifelse(x %in% names(mapping), mapping[x], x)
}

gdp_ranking %<>% rename_country1

marketcap %<>% 
  mutate(`Country Name` = rename_country2(`Country Name`)) %>% 
  select(-c(`Country Code`, `Indicator Name`, `Indicator Code`)) %>%
  pivot_longer(-`Country Name`, names_to = "Year", values_to = "Marketcap") %>%
  mutate(Year = as.numeric(Year)) %>%
  filter(`Country Name` %in% gdp_ranking)
```

```{r, eval = F}
stock_exchange = read_html("https://en.wikipedia.org/wiki/List_of_stock_exchanges", skip.rows = c(2, 18:27), which = 2, header = F, trim = T)

stock_exchange %<>% select(1:(match("Time zone", unlist(stock_exchange[1, ])) - 1))

names(stock_exchange) = stock_exchange %>% slice(1) %>% unlist

stock_exchange %<>% select(-1) %>% slice(-1) 

names(stock_exchange) %<>% str_replace_all("\\(.+\\)", "")

stock_exchange %<>% mutate(across(everything(), str_trim))

good = stock_exchange %>% filter(rowSums(is.na(.)) == 0) %>% select(Region, Year, `Market cap`)

bad = stock_exchange %>% filter(rowSums(is.na(.)) > 0) %>% filter(`Stock exchange` == "Nasdaq Nordic and Baltic Exchanges")

bad %<>% 
  mutate(Region = "Nasdaq Nordic",
         Year = bad %>% pull(which(map_lgl(bad, ~all(str_detect(., "20[0-9]{2}"))))),
         `Market cap` = bad %>% pull(which(map_lgl(bad, ~all(. == "Nasdaq Nordic and Baltic Exchanges"))) + 1)) %>%
  select(Region, Year, `Market cap`)

stock_exchange = bind_rows(good, bad) %>%
  rename(`Country Name` = Region, Marketcap = `Market cap`) %>%
  mutate(across(c(Year, Marketcap), ~str_replace_all(., ",", "") %>% as.numeric),
         `Country Name` = case_when(str_detect(`Country Name`, "United Kingdom") ~ "United Kingdom",
                                    `Country Name` == "European Union" ~ "Euronext",
                                    T ~ `Country Name`),
         Marketcap = Marketcap * 1e9) %>%
  group_by(`Country Name`, Year) %>%
  summarize(Marketcap = sum(Marketcap, na.rm = T)) %>%
  arrange(desc(Marketcap), desc(Year))

marketcap %<>% 
  full_join(stock_exchange %>% rename(Marketcap_wiki = Marketcap)) %>%
  mutate(Marketcap = case_when(is.na(Marketcap) ~ Marketcap_wiki,
                               T ~ Marketcap)) %>%
  select(-Marketcap_wiki) %>% 
  pivot_wider(id_cols = `Country Name`, names_from = Year, values_from = Marketcap) %>%
  pivot_longer(cols = -`Country Name`, names_to = "Year", values_to = "Marketcap") %>%
  mutate(Year = as.numeric(Year))
```

```{r}
marketcap %<>% 
  pivot_wider(id_cols = `Country Name`, names_from = Year, values_from = Marketcap) %>%
  pivot_longer(cols = -`Country Name`, names_to = "Year", values_to = "Marketcap") %>%
  mutate(Year = as.numeric(Year))

notNA_year = marketcap %>% group_by(Year) %>% summarise(notNA = sum(!is.na(Marketcap))) %>% filter(notNA > 0) %>% pull(Year)

marketcap %<>%
  filter(Year %in% notNA_year) %>%
  mutate(Marketcap = ifelse(is.na(Marketcap), 0, Marketcap)) %>%
  group_by(Year) %>%
  mutate(Proportion = Marketcap/sum(Marketcap)) %>%
  ungroup

top_country = marketcap %>% arrange(desc(Marketcap), desc(Year), desc(`Country Name`)) %>% pull(`Country Name`) %>% unique %>% .[1:3]
notNA_year = marketcap %>% filter(`Country Name` %in% top_country & Marketcap > 0) %>% count(Year) %>% filter(n == length(top_country)) %>% pull(Year) %>% tail(3)

major_country = marketcap %>% 
  filter(Year %in% notNA_year & Marketcap > 0) %>%
  group_by(`Country Name`) %>% 
  summarise(min_Proportion = min(Proportion)) %>% 
  pull(`Country Name`)

marketcap %<>%
  filter(`Country Name` %in% major_country & Year %in% notNA_year) %>%
  mutate(Proportion = case_when(Proportion == 0 ~ "No data", 
                                Proportion < 0.001 ~ "<0.1%",
                                T ~ make_percent(Proportion, 100))) %>%
  arrange(desc(Marketcap), desc(Year), desc(`Country Name`))

country_level = rev(unique(marketcap$`Country Name`))

marketcap %<>% mutate(`Country Name` = factor(`Country Name`, levels = country_level))
```

```{r, fig.height = (nrow(marketcap)/length(notNA_year) + 2)/4, fig.cap = str_c("Market capitalization of listed domestic companies across ", length(country_level), " major markets (approximate proportions of the global market capitalization are shown on the right side of each bar)")}
marketcap %>% 
  ggplot(mapping = aes(x = `Country Name`, y = Marketcap/1e12)) +
  geom_col(fill = brewer_pal("qual", 4)(2)[2], color = "black", width = 0.7) +
  geom_text(mapping = aes(y = Marketcap/1e12 + diff(range(Marketcap/1e12, na.rm = T))/35, label = Proportion), hjust = 0, size = 8 / .pt) + 
  scale_y_continuous(expand = c(0, 0, 0.23, 0)) +
  coord_flip() +
  labs(x = NULL, y = "Market capitalization ($trillion)") +
  theme(axis.ticks.y = element_blank()) +
  facet_grid(cols = vars(Year), scales = "free_x")
```

## GDP and market capitalization[^1]

```{r}
gdp_csv = unzip("gdp.zip", list = T) %>% pull(Name) %>% str_subset("^(?!Metadata)")
gdp = read_csv(file.path("gdp", gdp_csv), skip = 4, col_names = T, trim_ws = T)

gdp %<>% mutate(`Country Name` = rename_country2(`Country Name`)) %>%
  select(-c(`Country Code`, `Indicator Name`, `Indicator Code`)) %>% 
  pivot_longer(-`Country Name`, names_to = "Year", values_to = "GDP") %>%
  mutate(Year = as.numeric(Year)) %>%
  filter(Year >= (thisyear - 5) & `Country Name` %in% gdp_ranking)

country_level_rev = rev(intersect(country_level, gdp$`Country Name`))

combined = inner_join(gdp, marketcap) %>% 
  filter(Marketcap > 0) %>% 
  mutate(`Country Name` = factor(`Country Name`, levels = country_level_rev)) %>%
  arrange(desc(`Country Name`))

g = combined %>% 
  ggplot(mapping = aes(x = GDP/1e12, y = Marketcap/1e12)) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "gray") +
  geom_point(mapping = aes(color = `Country Name`), size = 3) +
  scale_x_continuous(trans = "log10") +
  scale_y_continuous(trans = "log10") +
  scale_color_manual(values = c(line_color[1:12], rep("black", length(country_level_rev) - 12)), guide = F) +
  labs(x = "GDP ($trillion)", y = "Market capitalization ($trillion)") +
  facet_grid(rows = vars(Year), scales = "free")

g2 = combined %>% 
  filter(`Country Name` %in% country_level_rev[1:13]) %>%
  ggplot(mapping = aes(x = GDP, y = Marketcap)) +
  geom_point(mapping = aes(color = `Country Name`), size = 3) +
  scale_x_continuous(trans = "log10") +
  scale_y_continuous(trans = "log10") +
  scale_color_manual(values = c(line_color[1:12], "black"), labels = c(country_level_rev[1:12], "Other countries"), guide = guide_legend(title = NULL)) +
  facet_grid(rows = vars(Year))

g_legend = get_legend(g2)

legend_padding = (theme_get()$legend.margin + theme_get()$legend.box.spacing)[4] %>% convertUnit("inch") %>% as.numeric
legend_key_width = theme_get()$legend.key.size %>% convertUnit("inch") %>% as.numeric
legend_label_width = c(country_level_rev[1:12], "Other countries") %>% stringWidth %>% convertUnit("inch") %>% max %>% as.numeric %>% multiply_by(0.8 * theme_get()$text$size/12)
legend_width = sum(legend_label_width, legend_key_width, legend_padding)
```

```{r buffett, fig.height = 5 * length(unique(combined$Year)) + 1/2, fig.cap = str_c("Market capitalization relative to GDP across ", length(unique(combined$`Country Name`)), " major countries")}
ggarrange(g, g_legend, widths = c(7 - legend_width, legend_width))
```

(ref:buffett-text) Same data as in Figure \@ref(fig:buffett)

```{r, fig.height = 5 * (7 - 1/2) / (7 - 1/2 - legend_width) * length(unique(combined$Year)) + 1/2, fig.cap = "(ref:buffett-text)"}
combined %>%
  mutate(`Country Name` = replace(as.character(`Country Name`), `Country Name` == "United States", "USA")) %>%
  ggplot(mapping = aes(x = GDP/1e12, y = Marketcap/1e12)) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "gray") +
  geom_text(mapping = aes(label = `Country Name`), hjust = 0.5, vjust = 0.5, size = 10 / .pt) +
  scale_x_continuous(trans = "log10") +
  scale_y_continuous(trans = "log10") +
  labs(x = "GDP ($trillion)", y = "Market capitalization ($trillion)") +
  facet_grid(rows = vars(Year), scales = "free")
```

## GDP and Buffett indicator[^2]

```{r}
Buffett = read_html("https://www.gurufocus.com/global-market-valuation.php", which = 3, header = T) %>% 
  mutate(across(-c(Country, `Country ETF`), as.numeric))
```

```{r, fig.cap = str_c("GDP and Buffett indicator across ", nrow(Buffett), " major countries")}
my_datatable(Buffett, paging = T, pageLength = 10, scrollY = NULL, caption = NULL)
```

## Market valuation[^2]

```{r}
USA = read_html("https://www.gurufocus.com/stock-market-valuations.php", header = T)
USA %<>% map(~{names(.) = str_trim(names(.)); mutate(., Country = "USA")})

country_mapping = c(China = "CHN",
                    Japan = "JPN",
                    Germany = "DEU",
                    India = "IND",
                    UK = "GBR",
                    France = "FRA",
                    Italy = "ITA", 
                    Canada = "CAN", 
                    Korea = "KOR", 
                    Australia = "AUS",
                    Spain = "ESP",
                    Russia = "RUS",
                    Brazil = "BRA",
                    Indonesia = "IDN")

USA = read_html("https://www.gurufocus.com/stock-market-valuations.php", header = T) %>%
  map(~{names(.) = str_trim(names(.)); mutate(., Country = "USA")})

plan(multisession)

Others = country_mapping %>%
  future_imap(~{
    tbl_list = read_html(str_c("https://www.gurufocus.com/global-market-valuation.php?country=", .x), which = -1, header = T)
    country = .y
    tbl_list %>% map(~{names(.) = str_trim(names(.)); mutate(., Country = country)})
  })

plan("default")

All = list.prepend(Others, USA = USA)

All %<>% 
  map_dfr(~{
    .[[which(map_lgl(., ~all(c("Ratio = Total Market Cap / GDP", "Valuation") %in% names(.))))]]
  }) %>%
  filter(`Ratio = Total Market Cap / GDP` %>% str_detect("Where are we today")) %>%
  mutate(Valuation = str_extract(Valuation, "(Significantly|Modestly|Fair) (Overvalued|Undervalued|valued)")) %>%
  select(-`Ratio = Total Market Cap / GDP`) %>%
  left_join(Buffett %>% select(Country, `Total Market/GDP Ratio (%)`, `GDP ($Trillion)`)) %>%
  rename(`Total Market/GDP Ratio` = "Total Market/GDP Ratio (%)") %>%
  arrange(`GDP ($Trillion)`) %>%
  mutate(Country = factor(Country, levels = Country),
         `Total Market/GDP Ratio` = `Total Market/GDP Ratio`/100,
         Valuation = str_to_sentence(Valuation) %>% factor(levels = c("Significantly overvalued", 
                                                                      "Modestly overvalued",
                                                                      "Fair valued",
                                                                      "Modestly undervalued",
                                                                      "Significantly undervalued")))
```

```{r, fig.height = (nrow(All) + 2)/4, fig.cap = str_c("Market valuation for ", nrow(All), " major countries")}
f1 = All %>% 
  ggplot(mapping = aes(x = Country, y = `GDP ($Trillion)`)) +
  geom_col(fill = brewer_pal("qual", 4)(2)[2], color = "black", width = 0.7) +
  scale_y_continuous(expand = c(0, 0, 0.05, 0)) +
  coord_flip() +
  labs(x = NULL, y = "GDP ($trillion)") +
  theme(axis.ticks.y = element_blank())

f2 = All %>% 
  ggplot(mapping = aes(x = Country, y = `Total Market/GDP Ratio`)) +
  geom_col(mapping = aes(fill = Valuation), color = "black", width = 0.7) +
  scale_y_continuous(expand = c(0, 0, 0.05, 0), labels = percent) +
  scale_fill_brewer(type = "qual", palette = 4, guide = guide_legend(title = NULL)) +
  coord_flip() +
  labs(x = NULL, y = "Total market/GDP ratio") +
  theme(axis.ticks.y = element_blank())

ggarrange(f1, f2, nrow = 1, legend = "right", common.legend = T)
```

## Projected annual return[^2]

```{r}
Project = read_html("https://www.gurufocus.com/global-market-valuation.php", which = 1, header = T) %>% 
  rename(Country = "") %>% 
  rename(`Projected Annual Return` = "Projected Annual Return (%)")

emerging = Project$Country[(which(Project$Country == "Emerging Market:") + 1):nrow(Project)]

Project %<>%
  filter(Country != "Emerging Market:") %>%
  mutate(Country = factor(Country, levels = rev(Country)),
         `Projected Annual Return` = str_replace(`Projected Annual Return`, "%", "") %>% as.numeric %>% divide_by(100))

cutoff = max(which(Project$Country %>% rev %>% as.character %in% emerging)) + 0.5
```

```{r, fig.height = (nrow(Project) + 2)/4, fig.cap = "Projected future annual returns of the world's 18 largest stock markets, calculated using (1) future business growth estimates, (2) dividends, and (3) change in market valuation"}
Project %>% ggplot(mapping = aes(x = Country, y = `Projected Annual Return`)) +
  annotation_custom(rectGrob(gp = gpar(col = "black", fill = "transparent")), xmin = cutoff) +
  annotation_custom(rectGrob(gp = gpar(col = "black", fill = "transparent")), xmax = cutoff) +
  annotation_custom(textGrob("Developed market", x = unit(0.95, "npc"), hjust = 1, vjust = -2, gp = gpar(fontface = "bold", fontfamily = "Lato")),
                    xmin = cutoff, xmax = cutoff) +
  annotation_custom(textGrob("Emerging market", x = unit(0.95, "npc"), hjust = 1, vjust = -2, gp = gpar(fontface = "bold", fontfamily = "Lato")),
                    xmin = -Inf, xmax = -Inf) +
  geom_col(mapping = aes(fill = factor(sign(`Projected Annual Return`), levels = c(-1, 1, 0))), color = "black", width = 0.7) +
  scale_y_continuous(breaks = pretty_breaks(), labels = percent) +
  scale_fill_brewer(type = "qual", palette = 4, guide = F) +
  coord_flip() +
  labs(x = NULL, y = "Projected annual return") +
  theme(axis.ticks.y = element_blank())
```

## U.S. stock market valuation

```{r}
Shiller = read_html("https://www.multpl.com/shiller-pe/table/by-month", which = 1, header = T) %>% 
  rename(date = Date,
         price = "\n\nValue\n\n\n\nValue\n") %>%
  mutate(date = as_date(date, format = "%b %e, %Y"),
         price = str_replace(price, "\\n\\nestimate", "") %>% as.numeric) %>%
  filter(date >= as_date(fiftyyearsago) - 30) %>%
  arrange(date)

SP500PER = read_html("https://www.multpl.com/s-p-500-pe-ratio/table/by-month", which = 1, header = T) %>% 
  rename(date = Date,
         price = "\n\nValue\n\n\n\nValue\n") %>%
  mutate(date = as_date(date, format = "%b %e, %Y"),
         price = str_replace(price, "\\n\\nestimate", "") %>% as.numeric) %>%
  filter(date >= as_date(fiftyyearsago) - 30) %>%
  arrange(date)

GDP = tq_get("GDP", get = "economic.data", from = as_date(fiftyyearsago) - 30) %>% 
  filter(!is.na(price)) %>%
  mutate(year = format(date, "%Y") %>% as.numeric,
         month = format(date, "%m") %>% as.numeric) %>%
  rename(GDP = price) %>%
  select(-c(date, symbol))

Wilshire5000 = tq_get("WILL5000PRFC", get = "economic.data", from = as_date(fiftyyearsago) - 30) %>% 
  filter(!is.na(price)) %>%
  mutate(year = format(date, "%Y") %>% as.numeric,
         month = format(date, "%m") %>% as.numeric,
         month = ((month - 1) %/% 3) * 3 + 1) %>%
  group_by(year, month) %>% 
  summarise(price = mean(price, na.rm = T)) %>%
  ungroup %>%
  rename(Wilshire5000 = price)

Buffett = full_join(GDP, Wilshire5000) %>% 
  mutate(price = Wilshire5000/GDP,
         date = make_date(year = year, month = month, day = 1)) %>%
  select(-c(GDP, Wilshire5000, year, month)) %>%
  filter(!is.na(price))
```

```{r, fig.height = 8/2.5, fig.cap = "Wilshire 5000 Full Cap Price Index/GDP"}
index_plot(Buffett, "Buffett indicator", from = as_date(fiftyyearsago) - 30)
```

(ref:shiller) [Cyclically adjusted P/E (CAPE) ratio for S&P 500](https://www.multpl.com/shiller-pe/)

```{r, fig.height = 8/2.5, fig.cap = "(ref:shiller)"}
index_plot(Shiller, "Shiller P/E ratio", from = as_date(fiftyyearsago) - 30)
```

(ref:sp500per) [S&P 500 P/E ratio, based on trailing 12 months "as reported" earnings](https://www.multpl.com/s-p-500-pe-ratio)

```{r, fig.height = 8/2.5, fig.cap = "(ref:sp500per)"}
index_plot(SP500PER, "S&P 500 P/E ratio", from = as_date(fiftyyearsago) - 30)
```

[^1]: Data are from [World Bank](https://data.worldbank.org/indicator/CM.MKT.LCAP.CD?view=chart) and [Wikipedia](https://en.wikipedia.org/wiki/List_of_stock_exchanges). Most recent 3 years for which top 3 countries\' data are available are shown.

[^2]: Source data and details can be found at [Gurufocus.com](https://www.gurufocus.com/global-market-valuation.php).
