# Asset growth simulation {#simulation}

In the Shiny web application embedded below, you can freely tune your investment scenario and see how your asset will grow over time. Specifically, you can choose 6 parameters depending on your financial situation:

1. Initial amount of investment
2. Investment amount per month
3. Increment of monthly investment per year
4. Your target annual profit
5. [Annual inflation rate](#inflation)
6. Total period of investment

## Simulation in USD

```{r, fig.cap = "Shiny web application for asset growth simulation in USD. The live version is available at https://junghoonshin.shinyapps.io/asset-growth-simulation-usd/."}
include_app("https://junghoonshin.shinyapps.io/asset-growth-simulation-usd/", height = "1000px")
```

## Simulation in KRW

```{r, fig.cap = "Shiny web application for asset growth simulation in KRW. The live version is available at https://junghoonshin.shinyapps.io/asset-growth-simulation-krw/."}
include_app("https://junghoonshin.shinyapps.io/asset-growth-simulation-krw/", height = "1000px")
```