# Small-cap list {#small-cap}

These are a list of relatively small-cap companies that interest me but need more research. Brief profile of each company is shown when available at [Wikipedia](https://en.wikipedia.org/wiki/Main_Page). Note that these profiles might be significantly outdated. For up-to-date comprehensive financial data, see Section \@ref(comprehensive).

```{r}
make_wikitable = function(name, which = 1) {
  wikitable = read_html(str_c("https://en.wikipedia.org/wiki/", name), which = which, header = T, trim = T) %>% 
    mutate(V2 = str_replace_all(V2, c("([A-Za-z])\\(" = "\\1 (",
                                      "\\[[0-9]+\\](?=(\\s+|$))" = ""))) %>%
    column_to_rownames("V1") %>% 
    t %>% 
    as_tibble
  
  missing = setdiff(c("Traded as", "Key people", "Products", "Services", "Industry", "Founders", "Subsidiaries"), names(wikitable))
  wikitable %<>% bind_cols(matrix(NA, nrow = 1, ncol = length(missing)) %>% set_colnames(missing) %>% as_tibble)
  
  wikitable %>%
    mutate(`Traded as` = str_replace_all(`Traded as`, "(.)(NYSE|NASDAQ|S&P|Russell)", "\\1<br>\\2")) %>%
    mutate(across(c(`Key people`, Services), ~str_replace_all(., c("\\)([A-Z])" = ")<br>\\1",
                                                                   "\\s*\\n\\s*" = "<br>"))),
           across(c(Industry, Founders, Products, Services, Subsidiaries), ~str_replace_all(., c("([a-z])([A-Z])" = "\\1<br>\\2",
                                                                                       ", " = "<br>",
                                                                                       ",* and " = "<br>")))) %>%
    t %>% 
    set_colnames("Val") %>%
    as_tibble(.name_repair = "minimal", rownames = "Var") %>%
    filter(!is.na(Val))
}

display_wikitable = function(wikitable, caption) {
  wikitable %>%
    kbl(escape = F, col.names = NULL, caption = caption) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),
                  full_width = F, position = "left")
}

image_link = function(image_file, url, ...) {
  a(href = url, img(src = image_file, ...))
}

marketcap = company_plot %>% select(Name_trimmed, Marketcap_USD)
```

## Intellia Therapeutics (`r marketcap %>% filter(Name_trimmed == "Intellia Therapeutics") %>% pull(Marketcap_USD) %>% make_readable %>% str_c(" $")`)

```{r}
image_link(image_file = "images/Intellia_Therapeutics.png", url = "https://www.intelliatx.com/", width = "240px")

wikitable = "Intellia_Therapeutics" %>% make_wikitable(1) 

wikitable %>% display_wikitable("Intellia Therapeutics")
```

## Nano-X Imaging (`r marketcap %>% filter(Name_trimmed == "Nano-X Imaging") %>% pull(Marketcap_USD) %>% make_readable %>% str_c(" $")`)

```{r}
image_link(image_file = "images/NanoX.svg", url = "https://www.nanox.vision/", width = "240px")
```

## Unity Software (`r marketcap %>% filter(Name_trimmed == "Unity Software") %>% pull(Marketcap_USD) %>% make_readable %>% str_c(" $")`)

```{r}
image_link(image_file = "images/Unity.png", url = "https://unity.com/", width = "240px")

wikitable = "Unity_Technologies" %>% make_wikitable(1)

wikitable$Val[wikitable$Var == "Subsidiaries"] %<>% 
  str_replace_all(c("Chilli<br>Connect" = "ChilliConnect",
                    "(.+)delta<br>DNA" = "\\1<br>deltaDNA",
                    "deltaDNA(.+)" = "deltaDNA<br>\\1"))

wikitable %>% display_wikitable("Unity Software")
```

## Parrot (`r marketcap %>% filter(Name_trimmed == "Parrot") %>% pull(Marketcap_USD) %>% make_readable %>% str_c(" $")`)

```{r}
image_link(image_file = "images/Parrot.png", url = "https://www.parrot.com/en", width = "240px")

wikitable = "Parrot_SA" %>% make_wikitable(7)

wikitable$Val[wikitable$Var == "Subsidiaries"] %<>% 
  str_replace_all(c("sense<br>Fly" = "senseFly"))

wikitable %>% display_wikitable("Parrot")
```

## Ambarella (`r marketcap %>% filter(Name_trimmed == "Ambarella") %>% pull(Marketcap_USD) %>% make_readable %>% str_c(" $")`)

```{r}
image_link(image_file = "images/Ambarella.png", url = "https://www.ambarella.com/", width = "240px")

wikitable = "Ambarella_Inc." %>% make_wikitable(1)

wikitable %>% display_wikitable("Ambarella")
```

## AeroVironment (`r marketcap %>% filter(Name_trimmed == "AeroVironment") %>% pull(Marketcap_USD) %>% make_readable %>% str_c(" $")`)

```{r}
image_link(image_file = "images/Aerovironment.png", url = "https://www.avinc.com/", width = "240px")

wikitable = "AeroVironment" %>% make_wikitable(1)

wikitable %>% display_wikitable("AeroVironment")
```

## Surface Oncology (`r marketcap %>% filter(Name_trimmed == "Surface Oncology") %>% pull(Marketcap_USD) %>% make_readable %>% str_c(" $")`)

```{r}
image_link(image_file = "images/Surface_Oncology.png", url = "https://www.surfaceoncology.com/", width = "240px")
```
